Capstone Movielens Report

### 2025-02-23 reports/capstone-movielens-report.draft2.Rmd
Genre effect accounting (in progress)

if(!require(gtools)) 
  install.packages("gtools")
if(!require(pak)) 
  install.packages("pak")

@@

library(rafalib)
library(gtools)
library(pak)

>>>>

if(!require(gtools)) 
  install.packages("gtools")
if(!require(pak)) 
  install.packages("pak")
if(!require("pacman")) 
  install.packages("pacman")

@@

library(rafalib)
library(gtools)
library(pak)
library(pacman)

p_load(latex2exp)
